Innovations Report: Procedural Fur System

### 2018-03-06 docs/paper.tex
more docs

\subsection{Resources} \label{sec:resources}
I decided to develop the API side of the fur system using C++, primarly as it most commonly used when developing computationally heavy artist tools, but also because it is the language I am most comfortable using. I opted to use OpenGL over other APIs (CUDA, OpenCL) for offloading of computation onto the GPU, simply because my final artefact is a tool with a graphical interface, and OpenGL is capable of handling both arbitary computation using compute shaders and rendering of geometry.

@@

@@

>>>>

\subsection{Resources} \label{sec:resources}
I decided to develop the API side of the fur system using C++, primarly as it most commonly used when developing computationally heavy artist tools, but also because it is the language I am most comfortable using. I opted to use OpenGL over other APIs (CUDA, OpenCL) for offloading of computation onto the GPU, simply because my final artefact is a tool with a graphical interface, and OpenGL is capable of handling both arbitary computation using compute shaders and rendering of geometry simultaneously.

@@

\subsection{Development} \label{sec:development}

write about obj loading

write about distributing https://stackoverflow.com/questions/9294316/distribute-points-on-mesh-according-to-density

write about GPU

@@

\subsection{Performance} \label{sec:performance}

insert stats comparing CPU/GPU compute
